# BCI Data - The critical transition between neutral and competitive communities 

I use BCI data to fit power law distribution of most abundant and not-most abundant species 



```{r setup, eval=T }
load(".RData")
#simul  <- F # variable to perform or not the simulations

oldcd <-getwd()
source("R/Neutral_fun.r")
source("R/BCI_fun.r")

# Set the location of the binary 
#
hkBin <- "~/Dropbox/cpp/SpatialAnalysis/Clusters/hk"
ClusterizeBin <- "~/Dropbox/cpp/SpatialAnalysis/XY2sed"

#neuBin64<- "~/Dropbox/cpp/CaNew/Neutral/ipsNeutralP64"
BCIwd <- "~/Dropbox/Data/BCI"

require(pander)
require(plyr)
require(dplyr)
panderOptions('table.split.table',Inf)
panderOptions('table.style', 'multiline')
options("scipen"=100, "digits"=6)
```

# Analysis of BCI data

* Discretize  x,y data into a lattice
* Fit patch distributions


```{r BCI_patch,echo=FALSE, eval=TRUE}



# pathnames <- list.files(pattern="[.]R$", path="R/", full.names=TRUE);
# sapply(pathnames, FUN=source);

# 1982
#

sa <-BCI_fit_plot('bci.full1.rdata','bci.full1',"BCI1982Sp", 1982,1000,500,1)
BCIMdl <- sa$BCIMdl
BCIhsize <- sa$BCIhsize


# 1985
#
sa <-BCI_fit_plot('bci.full2.rdata','bci.full2',"BCI1985Sp", 1985,1000,500,1)
BCIMdl <- rbind(BCIMdl,sa$BCIMdl)
BCIhsize <- rbind(BCIhsize,sa$BCIhsize)


# 1990
#
sa <-BCI_fit_plot('bci.full3.rdata','bci.full3',"BCI1990Sp", 1990,1000,500,1)
BCIMdl <- rbind(BCIMdl,sa$BCIMdl)
BCIhsize <- rbind(BCIhsize,sa$BCIhsize)


## 1995
#
sa <-BCI_fit_plot('bci.full4.rdata','bci.full4',"BCI1995Sp", 1995,1000,500,1)
BCIMdl <- rbind(BCIMdl,sa$BCIMdl)
BCIhsize <- rbind(BCIhsize,sa$BCIhsize)


# 2000
#
sa <-BCI_fit_plot('bci.full5.rdata','bci.full5',"BCI2000Sp", 2000,1000,500,1)
BCIMdl <- rbind(BCIMdl,sa$BCIMdl)
BCIhsize <- rbind(BCIhsize,sa$BCIhsize)


# 2005
#
sa <-BCI_fit_plot('bci.full6.rdata','bci.full6',"BCI2005Sp", 2005,1000,500,1)
BCIMdl <- rbind(BCIMdl,sa$BCIMdl)
BCIhsize <- rbind(BCIhsize,sa$BCIhsize)

## 2010
#
sa <-BCI_fit_plot('bci.full7.rdata','bci.full7',"BCI2010Sp", 2010,1000,500,1)
BCIMdl <- rbind(BCIMdl,sa$BCIMdl)
BCIhsize <- rbind(BCIhsize,sa$BCIhsize)


save.image()

```


# Plots of Biggest patch species 

We assume that BCI is at steady state and different studies point out that it should be close to a purely neutral dynamics [@Condit2012; @Seri2012; @Volkov2007]


```{r BCI_PlotPatch,echo=FALSE, eval=TRUE}

# Select Power w/exponential cutoff - spanning or most abundant  sp
#

require(ggplot2)

namType <- c("Spanning","MaxPatch","Other MaxPatch","Other Spanning")
namTypeAb <- c("Spanning/+Abundant","Spanning/+Abundant","Other Species","Other Species")
mc <- c("#E69F00", "#56B4E9", "#009E73", "#F0E442", "#0072B2", "#D55E00", "#CC79A7")

mMdl <- ungroup(BCIMdl) %>%  filter(model=="PowExp",type==1 | type==2) %>% mutate(typeAb=namTypeAb[type],type=namType[type])


# Plot of power exponent 
#
g <-ggplot(mMdl,aes(x=Year,y=alfa,colour=type)) + geom_point() +  theme_bw()+
    ylab(bquote(alpha)) + xlab("Year")+ scale_colour_manual(values=mc,guide=F)#+

g + stat_quantile(quantiles = 0.5) #+ coord_cartesian(ylim=c(-0.02,0.32))

ggsave("figs/discExpSpan_BCI.png", width=6,height=4,units="in",dpi=600)


# Plot Exponential rate - lambda of spanning or  most abundant sp
#
g <-ggplot(mMdl,aes(x=Year,y=rate,colour=type)) + geom_point() +  theme_bw() +
    ylab(bquote(lambda)) + xlab("Year") + scale_colour_manual(values=mc,guide=F)

g + stat_quantile(quantiles = 0.5) #+ coord_cartesian(ylim=c(-0.02,0.32))

ggsave("figs/discRateSpan_BCI.png", width=6,height=4,units="in",dpi=600)

# Quantile regression lambda
#
#
require(quantreg)

rq1 <-group_by(mMdl,type) %>%
      do(as.data.frame(do.call(rbind,
                               lapply(summary(rq(alfa~Year,data=.,tau=c(.25, .5, .75)),se="boot"),coef))
                       ,row.names= NULL)) %>% mutate(Tau=rep(c(.25, .5, .75),each=2),param="alpha")

rq1

rqm <-group_by(mMdl,type) %>%
      do(as.data.frame(do.call(rbind,
                               lapply(summary(rq(rate~Year,data=.,tau=c(.25, .5, .75)),se="boot"),coef))
                       ,row.names= NULL)) %>% mutate(Tau=rep(c(.25, .5, .75),each=2),param="lambda")

rqm <- rbind(rq1,rqm)

# Select Other MaxPatch
#
#
mMdl <- ungroup(BCIMdl) %>%  filter(model=="PowExp",type==3 | type==4) %>% mutate(typeAb=namTypeAb[type],type=namType[type])
#mMdl <- ungroup(BCIMdl) %>%  filter(type==3 | type==4)
# Plot Exponential rate - lambda of Other MaxPatch or spanning 
#
g <-ggplot(mMdl,aes(x=Year,y=rate,colour=as.factor(type))) + geom_point() +  theme_bw() + ylab(bquote(lambda)) + xlab("Year") + scale_y_log10()+guides(colour=FALSE)

g + stat_quantile(quantiles = 0.5) #+ coord_cartesian(ylim=c(-0.02,0.32))

ggsave("figs/discRateOther_BCI.png", width=7,height=4,units="in",dpi=600)


rq1 <-group_by(mMdl,type) %>%
      do(as.data.frame(do.call(rbind,
                               lapply(summary(rq(rate~Year,data=.,tau=c(.25, .5, .75)),se="boot"),coef))
                       ,row.names= NULL)) %>% mutate(Tau=rep(c(.25, .5, .75),each=2),param="lambda")


rqm <-rbind(rqm,rq1)

rq1 <-group_by(mMdl,type) %>%
      do(as.data.frame(do.call(rbind,
                               lapply(summary(rq(alfa~Year,data=.,tau=c(.25, .5, .75)),se="boot"),coef))
                       ,row.names= NULL)) %>% mutate(Tau=rep(c(.25, .5, .75),each=2),param="alpha")

rqm <-rbind(rqm,rq1)

rqm$slope<-c(F,T)
names(rqm)[5]<-"pvalue"
rqm <- filter(rqm, slope==T ) %>% select(type,param,Tau,Value:pvalue)

rqm
```

