# The critical transition between neutral and competitive communities 

I use here the following neutral model with power dispersal kernel:

<https://github.com/lsaravia/Neutral>

I generate parameter files for the simulation of neutral/hierarchical model using a uniform metacommunity distribution


```{r setup, eval=T }
load(".RData")
#simul  <- F # variable to perform or not the simulations

oldcd <-getwd()
source("R/Neutral_fun.r")

# Set the location of the binary 
#
neuBin <- "~/Dropbox/cpp/CaNew/Neutral/ipsNeutralPow"
neuBin64<- "~/Dropbox/cpp/CaNew/Neutral/ipsNeutralP64"


require(pander)
panderOptions('table.split.table',Inf)
options("scipen"=100, "digits"=4)
```

## Neutral Simulations to reach steady state

* near the critical point the transient is longer. 
  

* check criteria for steady state H? see @Keymer1998 Shannon entropy of the system remain bounded to very small fluctuations around a fixed value

Now I will simulate the model to Time=1500 with a full set of parameters 
Replacement = 0,0.001,0.01,0.1,1 and 30 repetitions 

The first thing is to generate the parameters to simulate

```{r gensimul30_LogSerParms, eval=T,echo=F,message=F,warning=F}
setwd("Simul")

# Ver Neutral_Model_BCI.Rmd 
#
m =  0.0001596079
alfa=2.038974
side <- 100
nsp <- 64
ReplRate <- 0.01   # c(0,0.001,0.01,0.05,0.1,1)
CT <- data.frame(MetaNsp=numeric(0),Side=numeric(0),Disp=numeric(0),Migr=numeric(0),Repl=numeric(0),TMaxH=numeric(0),MaxH=numeric(0),TMaxRich=numeric(0),MaxRich=numeric(0))

# loop con do paralell 
# ELIMINAR CALCULODQ************************************ 
CT <- rbind(CT,simul_NeutralPlotTime(nsp,side,alfa,m,ReplRate,T,2000,3))


# TMax 350 Repl 0.01 H 0.729 Rich 8

```


```{r simul30_LogSerParms, eval=F,echo=F,message=F,warning=F}
setwd("Simul")

# simul_NeutralPlotTime(8,256,T,500,"L")

ps <- data.frame(nsp=c(8,64,256),si=rep(c(512,256),each=3))
require(doParallel)
cn <-detectCores()
cl <- makeCluster(cn)
registerDoParallel(cl)

simul <- foreach(i=1:nrow(ps),.combine='rbind') %dopar%
{
    simulNeutral_1Time(ps$nsp[i],ps$si[i],500,"L",30,F)
}
stopCluster(cl)

setwd(oldcd)
rm(ps,cn,cl)
save.image()

```

## Calculate power of SAD DqSAD DqSRS using q=[-24,24]

Mortality=0.2
Dispersal=0.04
Colonization=0.001

```{r power_LogSerParms, eval=F,echo=F,message=F,warning=F}
setwd("Simul")

# Testing
#
#simul <- data.frame()
#sim1 <- rbind(simul,simulNeutral_1Time(65,256,100,"L",3))
#sim1 <- data.frame(nsp=65,side=256,time=100,meta="L",spMeta=87,rep=3)
#cc <- powerNeutral_1Time(simul[4,])

mm <- 0.2
dd <- 0.04
co <- 0.001

require(doParallel)
cn <-detectCores()
cl <- makeCluster(cn)
registerDoParallel(cl)
require(foreach)

cc <- foreach(i=1:nrow(simul)) %dopar%
{
    powerNeutral_1Time(simul[i,],mm, dd, co) # Mortality,Dispersal,Colonization
}
pow_ADq24 <- data.frame()
comp_ADq24<- data.frame()


for(i in 1:nrow(simul)) {
  pow_ADq24 <- rbind(pow_ADq24, cc[[i]]$pow_AD)
	comp_ADq24<- rbind(comp_ADq24,cc[[i]]$comp_AD)
}

rm(cc)

stopCluster(cl)

setwd(oldcd)
save.image()
```


DqSAD have higher power but also a very high type I error rate.
DqSRS have lower power and a lower type I error.
SAD have low power with a small number of species and a low type I error rate.


The power of the AD or KS test Depends on the number of points used so for SAD the number of species compared change the number of points used for the test, but for DqSRS and DqSAD the number of points is always q=35 thus so we could calculate more dimensions to raise the power of the test.


# Test usign glm which factors influence power

```{r testAD_factors, eval=F,echo=F,message=T,warning=T}
require(plyr)
hh <-function(x) {
  t <- nrow(x)
  s <- nrow(x[x$p.value<0.05,])
  data.frame(count=s,power=s/t,n=t)
}
# Calculate power
c1 <- with(comp_ADq24,comp_ADq24[MrtR1==MrtR2 & DspD1==DspD2 & ClnR1==ClnR2 & RplR2!=RplR1,])
c1$DifR <- with(c1,abs(RplR2-RplR1))
c2 <- ddply(c1,.(NumSp,Side,Type,DifR),hh)
#require(dplyr)
#c2 <- tbl_df(c1)
#c3 <- c2 %>% 
#  group_by(NumSp,Side,Type,MrtR1,DspD1,DifR) %>% 
#  filter(p.value<0.05) %>% 
#  summarize(tot=n()) %>% 
#  summarize(pgt5=n()) 
model1 <-glm(count~NumSp*Side*Type*DifR,poisson,data=c2)
summary(model1)
plot(model1)

# HAVE TO USE BINOMIAL !!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!1


```


# Use the information dimension t-test 

Fractal dimensions have several problems of estimation (Halley) so we use information dimension with sd estimated by the regression

```{r infoDim_Ttest, eval=F,echo=F,message=T,warning=T}
setwd("Simul")
#sim1 <- data.frame(nsp=65,side=256,time=100,meta="L",spMeta=87,rep=3)
# 256 = 7 points for Dq
#
#cc <- powerNeutral_1T_D1(sim1,7,1)

require(doParallel)
cn <-detectCores()
cl <- makeCluster(cn)
registerDoParallel(cl)
require(foreach)

cc <- foreach(i=1:nrow(simul)) %dopar%
{
    powerNeutral_1T_D1(simul[i,],log2(simul$side)-1,1,0.2,0.04,0.001)
}
pow_TD1 <- data.frame()
comp_TD1<- data.frame()

for(i in 1:nrow(simul)) {
  pow_TD1 <- rbind(pow_TD1, cc[[i]]$pow_AD)
  comp_TD1<- rbind(comp_TD1,cc[[i]]$comp_AD)
}
rm(cc)

stopCluster(cl)

setwd(oldcd)
save.image()


```
Calculate Power using compareGrowthCurves and q=-24,24

```{r power_GCtest, eval=F,echo=F,message=T,warning=T}
setwd("Simul")
# sim1 <- data.frame(nsp=65,side=256,time=100,meta="L",spMeta=87,rep=3)
#
#cc <- powerNeutral_1T_GC(simul[1,],3,0,0,0.001)

# Error en
# [1] "0.2_0.04_0.0001_1_1 4 0.2_0.04_0.0001_0.1_0 3"

require(doParallel)
cn <-detectCores()
cl <- makeCluster(cn)
registerDoParallel(cl)
require(foreach)

cc <- foreach(i=1:nrow(simul)) %dopar%
{
    powerNeutral_1T_GC(simul[i,],3,0.2,0.04,0.001)
}
pow_GC1 <- data.frame()
comp_GC1<- data.frame()

for(i in 1:nrow(simul)) {

  pow_GC1 <- rbind(pow_GC1, cc[[i]]$pow_AD)
  comp_GC1<- rbind(comp_GC1,cc[[i]]$comp_AD)
  }

stopCluster(cl)

setwd(oldcd)
rm(cc)
save.image()
```



More simulations to do comparisons with GC

```{r more_simul512_LogSerParms, eval=F,echo=F,message=F,warning=F}
setwd("Simul")

ps <- data.frame(nsp=c(8,64,256),si=rep(c(512,256),each=3))
require(doParallel)
cn <-detectCores()
cl <- makeCluster(cn)
registerDoParallel(cl)

simul <- foreach(i=1:nrow(ps),.combine='rbind') %dopar%
{
    simulNeutral_1Time(ps$nsp[i],ps$si[i],500,"L",20,F)
}
stopCluster(cl)

setwd(oldcd)
rm(ps,cn,cl)
save.image()
```


Compare using the GC with q<=10

```{r power_GCq10test, eval=F,echo=F,message=T,warning=T}
setwd("Simul")

require(doParallel)
cn <-detectCores()
cl <- makeCluster(cn)
registerDoParallel(cl)
require(foreach)

#] "0.2_0.04_0.001_1_1 3 0.2_0.04_0.001_1_3 3"
# Error: valor ausente donde TRUE/FALSE es necesario

cc <- foreach(i=1:nrow(simul)) %dopar%
{
    powerNeutral_1T_GC(simul[i,],3,0.2,0.04,0.001,10)
}
pow_GCq10 <- data.frame()
comp_GCq10<- data.frame()

for(i in 1:nrow(simul)) {

  pow_GCq10 <- rbind(pow_GCq10, cc[[i]]$pow_AD)
  comp_GCq10<- rbind(comp_GCq10,cc[[i]]$comp_AD)
  }

stopCluster(cl)

setwd(oldcd)
rm(cc)
save.image()

```

The power of compareGrowthCurves is much much greater using the range -10 10 than -24 24, and type I error is lower!!

Lets try with ANderson-Darling test!

```{r power_ADq10test, eval=F,echo=F,message=T,warning=T}
setwd("Simul")

require(doParallel)
cn <-detectCores()
cl <- makeCluster(cn)
registerDoParallel(cl)
require(foreach)

cc <- foreach(i=1:nrow(simul)) %dopar%
{
    powerNeutral_1Time(simul[i,],0.2,0.04,0.001,10)
}
pow_ADq10 <- data.frame()
comp_ADq10<- data.frame()

for(i in 1:nrow(simul)) {

  pow_ADq10 <- rbind(pow_ADq10, cc[[i]]$pow_AD)
  comp_ADq10<- rbind(comp_ADq10,cc[[i]]$comp_AD)
  }

stopCluster(cl)

setwd(oldcd)
rm(cc)
save.image()

```

# Make plots of power! using q=[-24,24]


```{r power_PlotAD, eval=F,echo=F,message=T,warning=T}

require(dplyr)
#pow_ADq24 <- with(pow_AD,pow_AD[MrtR==0.2 & DspD==0.04 & ClnR==0.001,])

# Select only the subset I will use
#
#pow_ADq24 <- filter(pow_AD,MrtR==0.2 & DspD==0.04 & ClnR==0.001) %>%
#  mutate(spMeta = ceiling(as.numeric(NumSp)*1.33)) 
 
plotPow_MeanSp_side(pow_ADq24)

ggsave("powADq24_MeanSp_Side.png", width=6,height=6,units="in",dpi=600)

require(pander)
pandoc.table(select(pow_ADq24,Side,spMeta,MeanSp, c(5:9)),style="grid",split.tables=Inf)


pow_ADq24 <- pow_ADq24 %>% mutate(NumSp=as.numeric(NumSp),MeanSp=as.numeric(MeanSp),Side=as.numeric(Side))

comp_ADq24 <- comp_AD %>% filter(MrtR1==0.2 & DspD1==0.04 & ClnR1==0.001) %>% 
  left_join(unique(pow_ADq24[,1:3]),by=c("Side","NumSp"))

plotPow_MeanSp_difR(comp_ADq24)

ggsave("powADq24_DifReplacement.png", width=6,height=6,units="in",dpi=600)



# Calculate TypeI error in fuction of replacement rate
#c1 <- with(comp_ADq24,comp_ADq24[MrtR1==MrtR2 & DspD1==DspD2 & ClnR1==ClnR2 & RplR2==RplR1,])
#c3 <- ddply(c1,.(NumSp,Type,RplR2),hh)
#names(c3)[4]<-"typeI"
#g <- ggplot(c3,aes(x=RplR2,y=typeI)) + geom_point(shape=19,aes(colour=as.factor(Type))) + facet_grid( NumSp ~ .)
#g+theme_bw()

#rm(c1,c2,c3)

```
## Plot power of D1 

```{r power_PlotD1T, eval=F,echo=F,message=T,warning=T}

require(dplyr)

#pow_TD1$spMeta <- ceiling(as.numeric(pow_TD1$NumSp)*1.33)

pow_TD1 <- pow_TD1 %>% select(-MeanSp) %>% 
  mutate(spMeta=ceiling(as.numeric(NumSp)*1.33),power=as.numeric(power),typeI=as.numeric(typeI)) %>% 
  left_join(unique(pow_ADq10[,1:3]),by=c("Side","NumSp"))
require(pander)
pandoc.table(  select(pow_TD1,Side,spMeta,MeanSp,c(4:8)),style="grid",split.tables=Inf)

plotPow_MeanSp_side(pow_TD1)

ggsave("powTD1_MeanSp_Side.png", width=6,height=6,units="in",dpi=600)

# Calculate power in fuction of replacement rate difference
# Falta cambiar NumSp por 
#comp_TD1$spMeta <- ceiling(as.numeric(comp_TD1$NumSp)*1.33)


pow_TD1 <- pow_TD1 %>% mutate(NumSp=as.numeric(NumSp),MeanSp=as.numeric(MeanSp),Side=as.numeric(Side))

comp_TD1 <- comp_TD1 %>% filter(MrtR1==0.2 & DspD1==0.04 & ClnR1==0.001) %>% 
  left_join(unique(pow_ADq10[,1:3]),by=c("Side","NumSp"))


plotPow_MeanSp_difR(comp_TD1)
ggsave("powTD1_DifReplacement.png", width=6,height=6,units="in",dpi=600)



```

The power of D1 in combination with a T-test is relatively low with a maximun of 0.6 for  


```{r power_PlotGC, eval=F,echo=F,message=T,warning=T}

#pow_GC1 <-merge(pow_GC1,unique(pow_ADq10[,1:3]),by.x=c(1,2),by.y=c(1,2),all.y=F)[,c(1:2,10,4:9)]
#names(pow_GC1)[3]<- "MeanSp"
require(dplyr)

pow_GC1 <- pow_GC1 %>% select(-MeanSp) %>% 
  mutate(spMeta=ceiling(as.numeric(NumSp)*1.33),power=as.numeric(power),typeI=as.numeric(typeI)) %>% 
  left_join(unique(pow_ADq24[,1:3]),by=c("Side","NumSp")) %>%
  select(Side,spMeta,MeanSp,c(4:8))

require(pander)
pandoc.table(pow_GC1,style="grid",split.tables=Inf)


plotPow_MeanSp_side(pow_GC1)

ggsave("powGC_spMeta_Side.png", width=6,height=6,units="in",dpi=600)

plotPow_MeanSp_difR(comp_GC1)

ggsave("powGC_DifReplacement.png", width=6,height=6,units="in",dpi=600)

```


```{r power_PlotADq10, eval=F,echo=F,message=T,warning=T}


#pow_GC1 <-merge(pow_GC1,unique(pow_ADq10[,1:3]),by.x=c(1,2),by.y=c(1,2),all.y=F)[,c(1:2,10,4:9)]
#names(pow_GC1)[3]<- "MeanSp"

plotPow_MeanSp_side(pow_ADq10)

ggsave("powADq10_MeanSp_Side.png", width=6,height=6,units="in",dpi=600)


require(plyr)
require(dplyr)
# DONE! in .RData
#
#pow_ADq10 <- pow_ADq10 %>% mutate(NumSp=as.numeric(NumSp),MeanSp=as.numeric(MeanSp),Side=as.numeric(Side))
#
#
#comp_ADq10 <- comp_ADq10 %>% filter(MrtR1==0.2 & DspD1==0.04 & ClnR1==0.001) %>% 
#  left_join(unique(pow_ADq10[,1:3]),by=c("Side","NumSp"))

p1 <- plotPow_MeanSp_difR(comp_ADq10)
ggsave("powADq10_DifR_256.png", width=6,height=6,units="in",dpi=600)

p2 <- plotPow_MeanSp_difR(comp_ADq10,512)
ggsave("powADq10_DifR_512.png", width=6,height=6,units="in",dpi=600)

p1 <- rbind(p1,p2)
p1 <- select(p1,Side,spMeta,Type:n) %>% arrange(Side,spMeta,Type,DifR) 
write.table(format(p1,digits=2), file = "Dq1.dat", sep = "  ", row.names = F,quote = F)

rm(p1,p2)

require(pander)
pandoc.table( mutate(pow_ADq10 ,spMeta=ceiling(as.numeric(NumSp)*1.33),power=as.numeric(power),typeI=as.numeric(typeI)) %>% select(Side,spMeta,MeanSp,c(5:9))
,style="grid",split.tables=Inf,round=4)
```

## Simulations to plot spatial patterns with different replacement Rate

```{r neutral_SpSimPlot256, eval=F,echo=F,message=T,warning=T}
setwd("Simul")


# meta = 64, side=250, time=500
sad64 <- simul_NeutralSAD(64,256,500)

# Plot of the spatial pattern for Neutral model with Logseries SAD with 8,64,256 species and side=512/256
#
#g <- plotNeutral_SpatPat(64,256,500,"L",c(0.1,1))
g <- plotNeutral_SpatPat(64,256,500,"L",c(0,0.01,0.1,1))
g


setwd("..")
ggsave("spat_NeuLog64_256.png", width=8,height=6,units="in",dpi=600)


# Plot Dq for simulations in txt files (NULL)
#

setwd("Simul")
plotNeutral_Dq(64,256,500,"L",NULL) # Null use previous simulations 
setwd("..")
ggsave("Dq_NeuLog64_256.png", width=8,height=4,units="in",dpi=600)

setwd("Simul")
plotNeutral_Dq(8,256,500,"L",NULL) # Null use previous simulations 
setwd("..")
ggsave("Dq_NeuLog8_256.png", width=8,height=4,units="in",dpi=600)

setwd("Simul")
plotNeutral_Dq(256,256,500,"L",NULL) # Null use previous simulations 
setwd("..")
ggsave("Dq_NeuLog256_256.png", width=8,height=4,units="in",dpi=600)

# Plot simulations for all metacommunities 
#
setwd("Simul")
plotNeutral_Dq(0,256,500,"L",NULL) # Null use previous simulations 
setwd("..")
ggsave("Dq_NeuLog_NumSp_256.png", width=8,height=8,units="in",dpi=600)

setwd("Simul")
plotNeutral_Dq(0,512,500,"L",NULL) # Null use previous simulations 
setwd("..")
ggsave("Dq_NeuLog_NumSp_512.png", width=8,height=8,units="in",dpi=600)


### Plot Average SAD!
setwd("Simul")
detach("package:dplyr", unload=TRUE)
den <- plotNeutral_SAD(0,256)

setwd("..")
ggsave("RAD_NeuLog_spMeta_256.png", width=8,height=6,units="in",dpi=600)


# Create table with R2 of neutral models Dq
#

setwd("Simul")
Dqq <- R2Neutral_Dq(256)
Dqq <- rbind(Dqq,R2Neutral_Dq(512))

Dqq <- arrange(Dqq,DqType,Side,spMeta,ReplacementRate,Freq60,Freq90) %>% select(DqType,Side,spMeta,meanSp,ReplacementRate,Freq60,Freq90)


setwd("..")

#write.table(format(Dqq,digits=2), file = "Dq1.dat", sep = "  ", row.names = F,quote = F)

require(pander)
pandoc.table(format(Dqq,digits=2),style="grid",split.tables=Inf)

# Table with mean number of species by replacement rate
#
Dqq <- select(Dqq,Side,spMeta,ReplacementRate,meanSp)

#write.table(format(Dqq,digits=2), file = "Dq1.dat", sep = "  ", row.names = F,quote = F)
pandoc.table(format(Dqq,digits=2),style="grid",split.tables=Inf)

rm(Dqq,Dqq1)
```
