# The critical transition between neutral and competitive communities 

## Estimation of early warnings using the Max patch proportion, variance and Skewness

I use here the following neutral model with power dispersal kernel:

<https://github.com/lsaravia/Neutral>

I generate parameter files for the simulation of neutral/hierarchical model using a uniform and a logseries metacommunity distribution  


```{r setup, eval=T }
load(".RData")

oldcd <-getwd()
source("R/Neutral_fun.r")

# Set the location of the binary 
#
neuBin <- "~/Dropbox/cpp/CaNew/Neutral/ipsNeutralPow"
neuBin64<- "~/Dropbox/cpp/CaNew/Neutral/ipsNeutralP64"


require(pander)
require(plyr)
require(dplyr)

panderOptions('table.split.table',Inf)
panderOptions('table.style', 'multiline')
options("scipen"=100, "digits"=6)
```

## Plots of Smax - Calculation of Early warnings based on the Max Cluster (Smax) - Ensemble Averages  - NOT INCLUDED IN THE PAPER!

```{r plotSmaxT20000_clu_side_64_meta_m0001, eval=F,echo=F,message=T,warning=T}

m   <-0.0001
alfa <-round(2.03897,5)
side <- 256
nsp <- 64
time <- 20000

require(plyr)
require(dplyr)
require(ggplot2)

# Select the critical points across sides (128,192,256) 
# 
k<-filter(rhoCritSide,Time==time,MetaNsp==nsp,DispersalDistance==round(mean_power(alfa),2),ColonizationRate==m,Side!=64)
k$MetaType <- factor(k$MetaType,labels=c("Logseries","Uniform"))


#
# Select clusters across sides (128,192,256)
#
tClusters <- Clusters %>% filter(MetaNsp==nsp,DispersalDistance==alfa,ColonizationRate==m,Side!=64)  %>% mutate(MetaType=factor(MetaType,labels=c("Logseries","Uniform")))

#
# Select colors 
#
require(RColorBrewer)
colp <-brewer.pal(8,"Dark2")


#
# Plot of Spanning clusters sizes with critical probability across side
#
ggplot(tClusters, aes(x=ReplacementRate, y=SpanningClust)) + geom_point(alpha=.1) + theme_bw() + scale_x_log10() + stat_summary(fun.y=mean,geom="line",colour=colp[1])+ facet_grid(Side ~ MetaType ) + ylab("Spanning Cluster Size") + xlab(bquote(rho)) + geom_vline(aes(xintercept=pcrit),k,colour=colp[6])
ggsave("figs/SpanClusRepl_T20000_64_side_meta_m0001.png", width=6,height=6,units="in",dpi=600)

#
# The same Plot in linear x scale 
#
ggplot(tClusters, aes(x=ReplacementRate, y=SpanningClust)) + geom_point(alpha=.1) + theme_bw() + xlim(0,1)  + stat_summary(fun.y=mean,geom="line",colour=colp[1])+ facet_grid(Side ~ MetaType ) + ylab("Spanning Cluster Size") + xlab(bquote(rho)) + geom_vline(aes(xintercept=pcrit),k,colour=colp[6])
ggsave("figs/SpanClusRepl_T20000_64_side_meta_m0001_lin.png", width=6,height=6,units="in",dpi=600)

#
# Plot of Max clusters proportion with critical probability across side 
#
ggplot(tClusters, aes(x=ReplacementRate, y=MaxClusterProp)) + geom_point(alpha=.1) + theme_bw() + scale_x_log10() + stat_summary(fun.y=mean,geom="line",colour=colp[1])+ facet_grid(Side ~ MetaType ) + ylab("Max. Cluster Size") + xlab(bquote(rho)) + geom_vline(aes(xintercept=pcrit),k,colour=colp[6])
ggsave("figs/MaxClusRepl_T20000_64_side_meta_m0001.png", width=6,height=6,units="in",dpi=600)

#
# Plot of Max clusters proportion with critical probability
#
ggplot(tClusters, aes(x=ReplacementRate, y=MaxClusterProp)) + geom_point(alpha=.1) + theme_bw() + xlim(0,1) + stat_summary(fun.y=mean,geom="line",colour=colp[1])+ facet_grid(Side ~ MetaType ) + ylab("Max. Cluster Size") + xlab(bquote(rho)) + geom_vline(aes(xintercept=pcrit),k,colour=colp[6])
ggsave("figs/MaxClusRepl_T20000_64_side_meta_m0001_lin.png", width=6,height=6,units="in",dpi=600)

# Select  Smax & Shannon diversity vs rho across ColonizationRate 
#
k<-filter(rhoCritSide,Time==time,MetaNsp==nsp,DispersalDistance==26.66,Side==256)
k$MetaType <- factor(k$MetaType,labels=c("Logseries","Uniform"))
tClusters <- Clusters %>% filter(MetaNsp==nsp,DispersalDistance==alfa,Side==256)  %>% mutate(MetaType=factor(MetaType,labels=c("Logseries","Uniform")))

#
# Smax vs rho
#
ggplot(tClusters, aes(x=ReplacementRate, y=MaxClusterProp)) + geom_point(alpha=.1) + theme_bw() + scale_x_log10() + stat_summary(fun.y=median,geom="line",colour=colp[1])+ facet_grid(ColonizationRate ~ MetaType,scales="free_y" )+xlab(bquote(rho)) + geom_vline(aes(xintercept=pcrit),k,colour=colp[6]) + ylab("Smax proportion")
ggsave("figs/SmaxvsRepl_T20000_64_256_meta_m.png", width=6,height=6,units="in",dpi=600)

#
# Smax vs rho in linear x scale 
#
ggplot(tClusters, aes(x=ReplacementRate, y=MaxClusterProp)) + geom_point(alpha=.1) + theme_bw() +  stat_summary(fun.y=median,geom="line",colour=colp[1])+ facet_grid(ColonizationRate ~ MetaType,scales="free_y" )+xlab(bquote(rho)) + geom_vline(aes(xintercept=pcrit),k,colour=colp[6]) + theme(panel.margin.x=unit(0.6, "lines"))
ggsave("figs/SmaxvsRepl_T20000_64_256_meta_m_lin.png", width=6,height=6,units="in",dpi=600)


#
# Smax vs H
#
ggplot(tClusters, aes(x=MaxClusterProp, y=H)) + geom_point(alpha=.1) + theme_bw() +  scale_x_log10() +  facet_grid(ColonizationRate ~ MetaType,scales="free_y" )
  
ggsave("figs/SmaxvsH_T20000_64_256_meta_m.png", width=6,height=6,units="in",dpi=600)


#
# Smax vs Richness 
#
ggplot(tClusters, aes(x=MaxClusterProp, y=Richness)) + geom_point(alpha=.1) + theme_bw() +  scale_x_log10() +  facet_grid(ColonizationRate ~ MetaType,scales="free_y" )

rm(kk,k,k1,p,mClusters,tClusters,Clu,rank)

```


## Plots of Smax - Calculation of Early warnings based on the Max Cluster (Smax) - Ensemble averages  - NOT INCLUDED IN THE PAPER!

```{r plotSmaxT20000_clu_side_64_meta_m1, eval=F,echo=F,message=T,warning=T}

m   <-0.0001
alfa <-round(2.03897,5)
side <- 256
nsp <- 320
time <- 20000

require(plyr)
require(dplyr)
require(ggplot2)


# Select  Smax & Shannon diversity vs rho across ColonizationRate 
#
k<-filter(rhoCritSide,Time==time,MetaNsp==nsp,DispersalDistance==26.66,Side==256)
k$MetaType <- factor(k$MetaType,labels=c("Logseries","Uniform"))

tClusters <- Clusters %>% filter(MetaNsp==nsp,DispersalDistance==alfa,Side==256,ColonizationRate!=0.1)  %>% mutate(MetaType=factor(MetaType,labels=c("Logseries","Uniform"))) %>% group_by(MetaNsp,Side,MetaType,ColonizationRate,DispersalDistance,ReplacementRate) %>% summarise(MaxClusterVar=var(MaxClusterProp),MaxClusterProp=mean(MaxClusterProp),n=n(),SpanningProb=sum(ifelse(SpanningSpecies>0,1,0))/n,SpanningClust=mean(SpanningClust))

require(RColorBrewer)
colp <-brewer.pal(8,"Dark2")

ggplot(tClusters, aes(x=ReplacementRate, y=MaxClusterProp)) + geom_point() + theme_bw() + scale_x_log10() +   facet_grid(ColonizationRate ~ MetaType,scales="free_y" ) +xlab(bquote(rho)) + geom_line(colour=colp[1]) + geom_vline(aes(xintercept=pcrit),k,colour=colp[6]) + ylab("Mean of max cluster size")+  theme(axis.text.x=element_text(angle=-30, vjust=0.9,hjust = 0.1)) 
ggsave("figs/SmaxvsRepl_T20000_320_256_meta_m.png", width=6,height=6,units="in",dpi=600)

ggplot(tClusters, aes(x=ReplacementRate, y=MaxClusterVar)) + geom_point() + theme_bw() + scale_x_log10() +   facet_grid(ColonizationRate ~ MetaType,scales="free_y" ) +xlab(bquote(rho)) + geom_line(colour=colp[1]) + geom_vline(aes(xintercept=pcrit),k,colour=colp[6]) + ylab("Variance of max cluster size")+  theme(axis.text.x=element_text(angle=-30, vjust=0.9,hjust = 0.1)) 
ggsave("figs/VarSmaxvsRepl_T20000_320_256_meta_m.png", width=6,height=6,units="in",dpi=600)


#
# Calculate fluctuations.
# 
require(fitdistrplus)
tClusters <- Clusters %>% filter(MetaNsp==nsp,DispersalDistance==alfa,Side==256,ColonizationRate!=0.1)  %>% mutate(MetaType=factor(MetaType,labels=c("Logseries","Uniform"))) %>% group_by(MetaNsp,Side,MetaType,ColonizationRate,DispersalDistance,ReplacementRate) %>% mutate( Mean_MaxClusterProp=mean(MaxClusterProp), Delta_MaxCluster=MaxClusterProp-Mean_MaxClusterProp)

# Plot fluctuations
#
ggplot(tClusters, aes(x=ReplacementRate, y=Delta_MaxCluster)) + geom_point(alpha=.1) + theme_bw() + scale_x_log10() +   facet_grid(ColonizationRate ~ MetaType,scales="free_y" ) +xlab(bquote(rho)) + stat_summary(fun.y=median,geom="line",colour=colp[1]) + geom_vline(aes(xintercept=pcrit),k,colour=colp[6]) + ylab("Fluctuations of max cluster size")+  theme(axis.text.x=element_text(angle=-30, vjust=0.9,hjust = 0.1)) 
ggsave("figs/DeltaSmaxvsRepl_T20000_320_256_meta_m.png", width=6,height=6,units="in",dpi=600)

# Variance of fluctuations
#
vClusters <- tClusters %>% summarise(varDelta_MaxCluster=var(Delta_MaxCluster))
ggplot(vClusters, aes(x=ReplacementRate, y=varDelta_MaxCluster)) + geom_point(size=1) + theme_bw() + scale_x_log10() +   facet_grid(ColonizationRate ~ MetaType,scales="free_y" ) +xlab(bquote(rho)) + geom_line(colour=colp[1]) + geom_vline(aes(xintercept=pcrit),k,colour=colp[6]) + ylab(expression(Variance~of~Delta~S[max]))+  theme(axis.text.x=element_text(angle=-30, vjust=0.9,hjust = 0.1)) 
ggsave("figs/VarDeltaSmaxvsRepl_T20000_320_256_meta_m.png", width=6,height=6,units="in",dpi=600)

# Skewness of fluctuations
#
sClusters <- tClusters %>% do(abs_skewness=(descdist(.$MaxClusterProp, discrete=FALSE, boot=500))$skewness)
sClusters$abs_skewness <- as.numeric(sClusters$abs_skewness)

ggplot(sClusters, aes(x=ReplacementRate, y=abs_skewness)) + geom_point(size=1) + theme_bw() + scale_x_log10() +   facet_grid(ColonizationRate ~ MetaType,scales="free_y" ) +xlab(bquote(rho)) + geom_vline(aes(xintercept=pcrit),k,colour=colp[6]) + ylab("Skewness of Delta Smax")+ geom_hline(yintercept = 0,colour=colp[1]) + theme(axis.text.x=element_text(angle=-30, vjust=0.9,hjust = 0.1)) 

ssClusters <-left_join(sClusters,k,by=c("MetaType","ColonizationRate","Side","MetaNsp")) %>% mutate(before=ifelse(ReplacementRate<pcrit,TRUE,FALSE))

ggplot(ssClusters, aes(x=ReplacementRate, y=abs_skewness,colour=before)) + geom_point(size=1) + theme_bw() + scale_color_manual(values=colp,guide=FALSE) + scale_x_log10() +   facet_grid(ColonizationRate ~ MetaType,scales="free_y" ) +xlab(bquote(rho)) + geom_vline(aes(xintercept=pcrit),k,colour=colp[6]) + ylab(expression(Skewness~of~Delta~S[max]))+ geom_hline(yintercept = 0,colour=colp[1]) + theme(axis.text.x=element_text(angle=-30, vjust=0.9,hjust = 0.1)) 
ggsave("figs/SkewDeltaSmaxvsRepl_T20000_320_256_meta_m.png", width=6,height=6,units="in",dpi=600)


```


## Simulate to estimate distributions of patch sizes statistics


```{r simuldisp26_cluAll_side_64_meta30_T20000, eval=F,echo=F,message=T,warning=T}
setwd(oldcd)
source("R/powerlaw/discpowerexp.R")
source("R/powerlaw/discexp.R")
source("R/powerlaw/powerexp.R")
source("R/powerlaw/exp.R")
source("R/powerlaw/pareto.R")
source("R/powerlaw/zeta.R")

setwd("Simul")


m <-  0.0001
alfa <- 2.038974
side <- 512
nsp <- 64
nSimul <- 4

# time     <- c(20000 ,20000 ,20000 ,20000 ,20000 ,20000, 15000)
# ReplRate <- c(0.0000,0.0001,0.0002,0.0003,0.0005,0.0010, 0.01)
time     <- c(20000)
ReplRate <- c(0.0004)

p <-expand.grid(disp=alfa,migr=m,repl=ReplRate,side=side,meta=c("U","L")) 

time <-rep(time, times=nrow(p)/length(time))

p <-cbind(p,time)

require(doParallel)
cn <-detectCores()
cl <- makeCluster(cn)
registerDoParallel(cl)
#Models <- data.frame()
Mdl <- data.frame()
Mdl <- foreach(i=1:nrow(p),.combine='rbind') %dopar%
{
  simulNeutral_Clusters(nsp,p$side[i],p$disp[i],p$migr[i],p$repl[i],"A",p$time[i],nSimul,TRUE,"N",p$meta[i],FALSE,2)
  #simulNeutral_Clusters(nsp,p$side[i],p$disp[i],p$migr[i],p$repl[i],"A",p$time[i],nSimul,FALSE,"N",p$meta[i],FALSE,2)
}
Mdl$Side <- side

stopCluster(cl)
setwd(oldcd)

Models <- Mdl
Models <- bind_rows(Models,Mdl)

rm(cn,cl,Mdl,p,mm,mMdl)

save.image()

```


# Plot the cluster sizes with fitted functions - NOT INCLUDED IN THE PAPER!
 
```{r plotFitdisp26_cluAll_side_64_meta30_T5000, eval=F,echo=F,message=T,warning=T}
source("R/powerlaw/discpowerexp.R")
source("R/powerlaw/discexp.R")
source("R/powerlaw/powerexp.R")
source("R/powerlaw/exp.R")
source("R/powerlaw/pareto.R")
source("R/powerlaw/zeta.R")

setwd("Simul")


m <-  0.0001
alfa <- 2.038974
side <- 256
nsp <- 64
nSimul <- 10

time     <- c(20000 ,20000 ,20000 ,20000 ,20000, 15000)
ReplRate <- c(0.0000,0.0001,0.0003,0.0005,0.0010, 0.01)
p <-expand.grid(disp=alfa,migr=m,repl=ReplRate,side=side,meta=c("U","L")) 
time <-rep(time, times=nrow(p)/length(time))
p <-cbind(p,time)

for(i in 1:nrow(p)){
  plotNeutral_Clusters(nsp,p$side[i],p$disp[i],p$migr[i],p$repl[i],p$time[i],p$meta[i],Models)
}
setwd(oldcd)

```

# Plot relation of power exponent/ exponential rate with ReplacementRate

```{r plotdisp26_cluAll_side_64_meta30_T20000, eval=F,echo=F,message=T,warning=T}
setwd(oldcd)

#
# Hacer grafico con proporcion de ajustes 
require(ggplot2)
require(plyr)
require(dplyr)
options("scipen"=100, "digits"=6)

Models <- ungroup(Models)
# Proportion of best models by model only
#
group_by(Models,Side,model) %>% filter(DeltaAIC==0,type==1 | type ==2)  %>% summarise(n=n()) %>% ungroup() %>% mutate(Frequency=n/sum(n))

# Number of simulations by rho
#
Models %>% group_by(MetaType,Side,ReplacementRate) %>% filter(DeltaAIC==0,type==1 | type==2,Side==512)  %>% summarise(n=n())


namType <- c("Spanning","MaxPatch","Other MaxPatch","Other Spanning")
namTypeAb <- c("Spanning/+Abundant","Spanning/+Abundant","Other Species","Other Species")

mMdl <- Models %>% group_by(model,type,ReplacementRate) %>% filter(DeltaAIC==0,type==1 | type==2,Side==512,model!="NoModel")  %>% summarise(n=n()) %>% ungroup() %>% mutate(Frequency=n/sum(n),type=namType[type])

mMdl <- bind_rows(mMdl,data.frame(model="Exp",type=unique(mMdl$type),n=0,Frequency=0,ReplacementRate=0)) 
mMdl$model <- factor(mMdl$model,levels=c("Exp","Pow","PowExp"))

mc <- c("#E69F00", "#56B4E9", "#009E73", "#F0E442", "#0072B2", "#D55E00", "#CC79A7")

ggplot(mMdl, aes(x=model,y=Frequency,fill=type)) + geom_bar(stat="identity") +  scale_fill_manual(values=mc,name="Species",breaks=c("Spanning","MaxPatch","Other Spanning","Other MaxPatch")) + theme_bw() + scale_x_discrete(labels=c("Exp.","Power","Power Exp.")) + xlab("") +theme(axis.text.x=element_text(angle=-30, vjust=0.9,hjust = 0.1))

#ggsave("figs/ClusBestModel_T20000_64_512.png", width=6,height=6,units="in",dpi=600)


ggplot(mMdl, aes(x=ReplacementRate,y=Frequency,fill=model)) + geom_bar(stat="identity") +  scale_fill_manual(values=mc,name="",labels=c("Exp.","Power","Power Exp.")) + theme_bw() + theme(axis.text.x=element_text(angle=-30, vjust=0.9,hjust = 0.1)) +  scale_x_continuous(breaks=c(0.0000,0.0001,0.0002,0.0003,0.0005,0.0010, 0.01))  + xlab(bquote(rho))
ggsave("figs/ClusBestModel_T20000_64_512_rho.png", width=6,height=6,units="in",dpi=600)

# Make table by model
#
mm <- Models %>% group_by(model,type) %>% filter(DeltaAIC==0,type==1 | type==2,Side==512)  %>% summarise(n=n()) %>% ungroup() %>% mutate(Frequency=n/sum(n),type=namType[type])

require(pander)
pandoc.table(mm %>% mutate_if(is.numeric,round,digits=2))


# General linear model on alfa
#
mm <- filter(Models,model!="NoModel",Side==512,type==1 | type ==2,DeltaAIC==0) %>% mutate(type=namType[type])


am <-lm(alfa ~ MetaType*model*ReplacementRate,data=mm)
summary(am)

re <-resid(am)
plot(am, which=1)
plot(am, which=2)

am1 <- update(am, ~. -MetaType:model:ReplacementRate)
summary(am1)
anova(am1,am)

am2 <- update(am1, ~. -MetaType:model  )
summary(am2)
anova(am1,am2)
AIC(am,am1,am2)


# Kruskal wallis test on alfa
#

kruskal.test(alfa~factor(MetaType),data=mm)
kruskal.test(alfa~factor(model),data=mm)
kruskal.test(alfa~factor(type),data=mm)
kruskal.test(alfa~factor(ReplacementRate),data=mm)

boxplot(mm$alfa~mm$MetaType)
boxplot(mm$alfa~mm$model)
boxplot(mm$alfa~mm$type)
boxplot(mm$alfa~mm$ReplacementRate)

#
# No differences between Metacommunity or type (Spanning or max patch)
#
# Make a table with average parameter values
#
names(mm)
mm <- mm %>% group_by(model,ReplacementRate)  %>% summarise(n=n(),xmin=mean(xmin),alfa=mean(alfa),rate=mean(rate)) %>%  arrange(model,ReplacementRate)

require(pander)
options("scipen"=100, "digits"=4)
pandoc.table(mm %>%  mutate_if(is.numeric,round,digits=4))

# Plot power exponent alpha
#
mMdl <- filter(Models,model=="PowExp" | model == "Pow",type==1 | type==2, DeltaAIC==0) %>% mutate(typeAb=namTypeAb[type],type=namType[type])

ggplot(mMdl,aes(x=ReplacementRate,y=alfa,colour=model)) +  geom_jitter(size=0.5,width=0.00001) + theme_bw() + facet_grid(~MetaType)+ stat_summary(fun.y=median,geom="line") + scale_x_continuous(breaks=c(0.0000,0.0001,0.0002,0.0003,0.0005,0.0010, 0.01)) +
 theme(axis.text.x=element_text(angle=-30, vjust=0.9,hjust = 0.1)) + ylab(bquote(alpha)) + xlab(bquote(rho)) + scale_colour_manual(values=mc)+ coord_cartesian(ylim=c(1.5,5)) 

ggsave("figs/AlfaVsRho_T20000_64_512_meta.png", width=7,height=4,units="in",dpi=600)



# Plot Exponential decay rate of PowExp model
#
mMdl <- filter(Models,model=="PowExp" ,type==1 | type==2) %>%  mutate(typeAb=namTypeAb[type],type=namType[type])

ggplot(mMdl,aes(x=ReplacementRate,y=rate)) +  geom_point(size=0.5,colour=mc[2]) + theme_bw() +   stat_summary(fun.y=median,geom="line",colour=mc[2]) + facet_grid(~MetaType) + scale_x_continuous(breaks=c(0.0000,0.0001,0.0002,0.0003,0.0005,0.0010, 0.01)) +
  theme(axis.text.x=element_text(angle=-30, vjust=0.9,hjust = 0.1))  + ylab("Exp. decay rate") + xlab(bquote(rho)) +   coord_cartesian(ylim=c(0,.2))
ggsave("figs/ExpRateVsRho_T20000_64_512_meta.png", width=7,height=4,units="in",dpi=600)
 
# Eliminate duplicates from Models
#
mm <- Models %>% group_by(Side,MetaType,ReplacementRate,type,Rep,nPatches) %>% summarise(n=n()) %>% filter(n==1)
mm1<- inner_join(Models,mm)
mm2 <- mm1 %>% group_by(Side,MetaType,ReplacementRate,type,Rep,nPatches) %>% slice(1) 
nrow(Models)
Models <- anti_join(Models,mm1)
Models <- bind_rows(Models,select(mm2,1:18))
  
Models <- Models %>% group_by(Side,MetaType,ReplacementRate,type,Rep,nPatches) %>% slice(1:3)
mm2 <- mm1 %>% group_by(Side,MetaType,ReplacementRate,type,Rep,nPatches) %>% summarise(n=n())  
mm <- Models %>% filter(Side==256,ReplacementRate==0.001,Rep==1) %>% arrange(nPatches)
rm(mMdl,mm)
```


## Time series simulations for side=256 time=20000 logseries metacomunity filled initial conditions  m=0.0001

```{r timeSeries256_320__T20000Filled0001, eval=T,echo=F,message=F,warning=F}
setwd("Simul")

# Ver Neutral_Model_BCI.Rmd por parametros
#
m =  0.0001
alfa=2.038974
side <- 256
nsp <- 320
nSimul <- 10
timeInit <-1
timeDelta <- 100
rndI <- 11

# Interval where the critical transition occurs for rndI=11
#
# ReplRate <- c(0.0004,0.0005,0.0010,0.0100,0.02,0.05)
# time<-      c(22000, 26500,11500,  1300, 1100, 500)
# timeI<-     c(21400, 25900,10900,   800,  500, 1)   

ReplRate <- c(0.0000,0.0001,0.0002,0.00025,0.0003,0.0004,0.0005,0.0010,0.0050,0.0100,0.0500,0.1000,0.5000,1)
time <-     c(20000,  20000, 30000,  30000, 30000, 30000, 30000, 20000, 20000,20000,   5000,  5000,  5000,5000)
timeI<-     c(15000,  15000, 25000,  25000, 25000, 25000, 25000, 15000, 15000,15000,   0500,  0500,  0500,0500)


p <-expand.grid(disp=alfa,migr=m,repl=ReplRate,side=side,meta=c("U"),rndI=rndI)
time <-rep(time, times=nrow(p)/length(time))
p <-cbind(p,time)
timeI <-rep(timeI, times=nrow(p)/length(time))
p <-cbind(p,timeI)


require(doParallel)
cn <-detectCores()-1
cl <- makeCluster(cn)
registerDoParallel(cl)

#TSeriesCT <- data.frame()
TS1 <- data.frame()

TS1 <- foreach(i=1:length(ReplRate),.combine='rbind') %dopar%
{
    simul_NeutralTimeSeries(nsp,p$side[i],p$disp[i],p$migr[i],p$repl[i],TRUE,p$time[i],nSimul,"N",p$meta[i],"S",2,p$timeI[i],timeDelta,p$rndI[i],TRUE)
  
}
stopCluster(cl)

# Recover TS1 from files
#
# for(i in 1:length(ReplRate)){
#   TS1 <- bind_rows(TS1, simul_NeutralTimeSeries(nsp,p$side[i],p$disp[i],p$migr[i],p$repl[i],FALSE,p$time[i],nSimul,"N",p$meta[i],"S",2,p$timeI[i],timeDelta,p$rndI[i],TRUE))
# }

TSeriesCT <- rbind(TSeriesCT,TS1)

setwd(oldcd)

rm(kk,TS1,cl,cn,p)
save.image()
```

## Plots of Smax - Calculation of Early warnings based on the Max Cluster (Smax)

```{r plotSmaxT20000_clu_256_320_meta_m0001, eval=F,echo=F,message=T,warning=T}

m   <-0.0001
alfa <-round(2.03897,5)
side <- 256
nsp <- 320
time <- 20000

require(plyr)
require(dplyr)
require(ggplot2)

names(TSeriesCT)

# 
TS1 <- TSeriesCT %>% filter(MetaNsp==nsp,DispersalDistance==alfa,Side==256,ColonizationRate==0.0001)  %>% mutate(MetaType=factor(MetaType,labels=c("Logseries","Uniform"))) %>% group_by(MetaNsp,Side,MetaType,ColonizationRate,DispersalDistance,ReplacementRate,Rep) %>% 
  mutate(isSpan = any(SpanningSpecies != 0),constSpan=length(unique(SpanningSpecies))==1,
         posCP=ifelse(isSpan & constSpan,"After",
        ifelse(isSpan & !constSpan,"Near","Before"))) 


# Select  Smax & Shannon diversity vs rho across ColonizationRate 
#
k<-filter(rhoCritSide,Time==time,MetaNsp==nsp,DispersalDistance==26.66,Side==256,ColonizationRate==m)
k$MetaType <- factor(k$MetaType,labels=c("Logseries","Uniform"))

tClusters <- TS1 %>% #filter( isSpan==TRUE | ReplacementRate<0.0002) %>%
  group_by(MetaNsp,Side,MetaType,ColonizationRate,DispersalDistance,ReplacementRate,Rep) %>% summarise(MaxClusterVar=var(MaxClusterProp),MaxClusterProp=mean(MaxClusterProp),n=n())

require(RColorBrewer)
colp <-brewer.pal(8,"Dark2")

ggplot(tClusters, aes(x=ReplacementRate, y=MaxClusterProp)) + geom_point() + theme_bw() + scale_x_log10() +   facet_grid(~ MetaType,scales="free_y" ) +xlab(bquote(rho)) + stat_summary(fun.y=median,geom="line",colour=colp[1]) + geom_vline(aes(xintercept=pcrit),k,colour=colp[6]) + ylab("Mean of max cluster size")+  theme(axis.text.x=element_text(angle=-30, vjust=0.9,hjust = 0.1)) 
#ggsave("figs/SmaxvsRepl_T20000_320_256_meta_m.png", width=6,height=6,units="in",dpi=600)

ggplot(tClusters, aes(x=ReplacementRate, y=MaxClusterVar)) + geom_point() + theme_bw() + scale_x_log10() +   facet_grid(ColonizationRate ~ MetaType,scales="free_y" ) +xlab(bquote(rho)) + stat_summary(fun.y=median,geom="line",colour=colp[1]) + geom_vline(aes(xintercept=pcrit),k,colour=colp[6]) + ylab("Variance of max cluster size")+  theme(axis.text.x=element_text(angle=-30, vjust=0.9,hjust = 0.1)) 
#ggsave("figs/VarSmaxvsRepl_T20000_320_256_meta_m.png", width=6,height=6,units="in",dpi=600)


#
# Calculate fluctuations.
# 
tClusters <- TS1  %>% #filter(isSpan==TRUE | ReplacementRate<0.0002) %>%
  group_by(MetaNsp,Side,MetaType,ColonizationRate,DispersalDistance,ReplacementRate,Rep) %>% mutate( Mean_MaxClusterProp=mean(MaxClusterProp), Delta_MaxCluster=MaxClusterProp-Mean_MaxClusterProp,Mean_MaxClusterSpProp=mean(MaxClusterSpProp), Delta_MaxClusterSp=MaxClusterSpProp-Mean_MaxClusterSpProp)


# Plot fluctuations
#
options("scipen"=100, "digits"=4)

ggplot(tClusters, aes(x=ReplacementRate, y=Delta_MaxCluster)) + geom_point(alpha=.1) + theme_bw() + scale_x_log10(breaks=c(0.0000,0.0001,0.0002,0.0003,0.0005,0.0010, 0.01)) +   facet_grid(ColonizationRate ~ MetaType,scales="free_y" ) +xlab(bquote(rho)) + stat_summary(fun.y=median,geom="line",colour=colp[1]) + geom_vline(aes(xintercept=pcrit),k,colour=colp[6]) + ylab("Fluctuations of max cluster size")+  theme(axis.text.x=element_text(angle=-30, vjust=0.9,hjust = 0.1)) 
                                                                                                                  ggsave("figs/DeltaTSmaxvsRepl_T20000_320_256_meta_m.png", width=6,height=6,units="in",dpi=600)

# Variance of fluctuations
#
vClusters <- tClusters %>% summarise(varDelta_MaxCluster=var(Delta_MaxCluster),varDelta_MaxClusterSp=var(Delta_MaxClusterSp))

ggplot(vClusters, aes(x=ReplacementRate, y=varDelta_MaxCluster)) + geom_point(alpha=.1) + theme_bw() + scale_x_log10(breaks=c(0.0000,0.0001,0.0002,0.0003,0.0005,0.0010, 0.01)) +   facet_grid(~ MetaType,scales="free_y" ) +xlab(bquote(rho)) +stat_summary(fun.y=median,geom="line",colour=colp[1]) + geom_vline(aes(xintercept=pcrit),k,colour=colp[6]) + ylab(expression(Variance~of~Delta~S[max]))+  theme(axis.text.x=element_text(angle=-30, vjust=0.9,hjust = 0.1)) + coord_cartesian(ylim=c(0,.10))
ggsave("figs/VarDeltaTSmaxvsRepl_T20000_320_256_meta_m.png", width=7,height=4,units="in",dpi=600)

ggplot(vClusters, aes(x=ReplacementRate, y=varDelta_MaxClusterSp)) + geom_point(alpha=.1) + theme_bw() + scale_x_log10(breaks=c(0.0000,0.0001,0.0002,0.0003,0.0005,0.0010, 0.01)) +   facet_grid(~ MetaType,scales="free_y" ) +xlab(bquote(rho)) +stat_summary(fun.y=median,geom="line",colour=colp[1]) + geom_vline(aes(xintercept=pcrit),k,colour=colp[6]) + ylab(expression(Variance~of~Delta~RS[max]))+  theme(axis.text.x=element_text(angle=-30, vjust=0.9,hjust = 0.1)) + coord_cartesian(ylim=c(0,.10))
ggsave("figs/VarDeltaTSmaxSpvsRepl_T20000_320_256_meta_m.png", width=7,height=4,units="in",dpi=600)


# Skewness of fluctuations
#
require(fitdistrplus)

sClusters <- tClusters %>% do(abs_skewness=(descdist(.$MaxClusterProp, discrete=FALSE, boot=500))$skewness)
sClusters$abs_skewness <- as.numeric(sClusters$abs_skewness)

ggplot(sClusters, aes(x=ReplacementRate, y=abs_skewness)) + geom_point(size=1) + theme_bw() + scale_x_log10() +   facet_grid(ColonizationRate ~ MetaType,scales="free_y" ) +xlab(bquote(rho)) + geom_vline(aes(xintercept=pcrit),k,colour=colp[6]) + ylab(expression(Skewness~of~Delta~S[max]))+  geom_hline(yintercept = 0,colour=colp[1]) + theme(axis.text.x=element_text(angle=-30, vjust=0.9,hjust = 0.1)) 

ssClusters <-left_join(sClusters,k,by=c("MetaType","ColonizationRate","Side","MetaNsp")) %>% mutate(before=ifelse(ReplacementRate<pcrit,TRUE,FALSE))

ggplot(ssClusters, aes(x=ReplacementRate, y=abs_skewness,colour=before)) + geom_point(size=1) + theme_bw() + scale_color_manual(values=colp,guide=FALSE) + scale_x_log10() +   facet_grid(ColonizationRate ~ MetaType,scales="free_y" ) +xlab(bquote(rho)) + geom_vline(aes(xintercept=pcrit),k,colour=colp[6]) + ylab(expression(Skewness~of~Delta~S[max]))+ geom_hline(yintercept = 0,colour=colp[1]) + theme(axis.text.x=element_text(angle=-30, vjust=0.9,hjust = 0.1)) + stat_summary(fun.y=median,geom="line",colour=colp[4])
ggsave("figs/SkewDeltaTSmaxvsRepl_T20000_320_256_meta_m.png", width=6,height=6,units="in",dpi=600)


rm(ssClusters,sClusters,tClusters,vClusters)


#
# Plots before, in the transition, and after
# 
#
# Calculate fluctuations.
# 
vClusters <- TS1  %>% group_by(MetaNsp,Side,MetaType,ColonizationRate,DispersalDistance,ReplacementRate,posCP,Rep) %>% mutate( Mean_MaxClusterProp=mean(MaxClusterProp), Delta_MaxCluster=MaxClusterProp-Mean_MaxClusterProp,Mean_MaxClusterSpProp=mean(MaxClusterSpProp), Delta_MaxClusterSp=MaxClusterSpProp-Mean_MaxClusterSpProp) %>% summarise(varDelta_MaxCluster=var(Delta_MaxCluster),varDelta_MaxClusterSp=var(Delta_MaxClusterSp)) %>% ungroup() %>% mutate(posCP=factor(posCP,levels=c("Before","Near","After")))


ggplot(vClusters, aes(x=posCP, y=varDelta_MaxCluster,colour=posCP)) + geom_boxplot() + geom_jitter(width=0.2)+ theme_bw() + facet_grid(~ MetaType) + ylab(expression(Variance~of~Delta~S[max]))+  theme(axis.text.x=element_text(angle=-30, vjust=0.9,hjust = 0.1)) + scale_color_manual(values=colp,guide=FALSE) + xlab("")

ggsave("figs/VarDeltaTSmaxvsCP_T20000_320_256_meta.png",  width=7,height=4,units="in",dpi=600)

ggplot(vClusters, aes(x=posCP, y=varDelta_MaxClusterSp,colour=posCP)) + geom_boxplot() + geom_jitter(width=0.2)+ theme_bw() + facet_grid(~ MetaType) + ylab(expression(Variance~of~Delta~RS[max]))+  theme(axis.text.x=element_text(angle=-30, vjust=0.9,hjust = 0.1)) + scale_color_manual(values=colp,guide=FALSE) + xlab("")

ggsave("figs/VarDeltaTRSmaxvsCP_T20000_320_256_meta.png",  width=7,height=4,units="in",dpi=600)


#
# Skewness of fluctuations DeltaSmax
#
tClusters <- TS1  %>% group_by(MetaNsp,Side,MetaType,ColonizationRate,DispersalDistance,ReplacementRate,posCP,Rep) %>% mutate( Mean_MaxClusterProp=mean(MaxClusterProp), Delta_MaxCluster=MaxClusterProp-Mean_MaxClusterProp,Mean_MaxClusterSpProp=mean(MaxClusterSpProp), Delta_MaxClusterSp=MaxClusterSpProp-Mean_MaxClusterSpProp)

#
require(fitdistrplus)
sClusters <- tClusters %>% do(abs_skewness=(descdist(.$Delta_MaxCluster, discrete=FALSE, boot=500))$skewness)
sClusters <- sClusters %>% mutate(abs_skewness=as.numeric(abs_skewness),posCP=factor(posCP,levels=c("Before","Near","After")))

ggplot(sClusters, aes(x=posCP, y=abs_skewness,colour=posCP)) + geom_boxplot() + geom_jitter(width=0.2)+ theme_bw() + facet_grid(~ MetaType) + ylab(expression(Skewness~of~Delta~S[max]))+  theme(axis.text.x=element_text(angle=-30, vjust=0.9,hjust = 0.1)) + scale_color_manual(values=colp,guide=FALSE) + xlab("") +  geom_hline(yintercept = 0,colour="darkgrey")
ggsave("figs/SkewDeltaTSmaxvsCP_T20000_320_256_meta.png", width=7,height=4,units="in",dpi=600)


#
# Skewness of DeltaRSmax 
#
sClusters <- tClusters %>% do(abs_skewness=(descdist(.$Delta_MaxClusterSp, discrete=FALSE, boot=500))$skewness)
sClusters <- sClusters %>% mutate(abs_skewness=as.numeric(abs_skewness),posCP=factor(posCP,levels=c("Before","Near","After")))

ggplot(sClusters, aes(x=posCP, y=abs_skewness,colour=posCP)) + geom_boxplot() + geom_jitter(width=0.2)+ theme_bw() + facet_grid(~ MetaType) + ylab(expression(Skewness~of~Delta~RS[max]))+  theme(axis.text.x=element_text(angle=-30, vjust=0.9,hjust = 0.1)) + scale_color_manual(values=colp,guide=FALSE) + xlab("") +  geom_hline(yintercept = 0,colour="darkgrey")
ggsave("figs/SkewDeltaTRSmaxvsCP_T20000_320_256_meta.png", width=7,height=4,units="in",dpi=600)


```


# Simulations to make a video of percolation

```{r gensimul_spat_256_32_meta30_T5000, eval=F,echo=F,message=T,warning=T}
setwd("Simul")

m   <-  0.0001
alfa<-  2.038974
side <- 256
nsp <-  64
nSimul <- 1


ReplRate <- c(0.0003)
time <- 3000

require(animation)
# simul_NeutralSpatPatt <- function(nsp,side,disp,migr,repl,clus="S",time=1000,inter=10,init=1,meta="L",delo=F,sim=T,sedIni=0,modType=4,death=0.2,birth=1,colPal=0) 

simul_NeutralSpatPatt(nsp,side,alfa,m,ReplRate,"S",time,10,100,"L",T,T,2)

saveGIF(simul_NeutralSpatPatt(nsp,side,alfa,m,ReplRate,"S",1000,10,800,"L",T,F), 
        interval = .3, 
        movie.name=paste0("neuL",nsp,"_",side,"R", ReplRate,".gif")
)


ReplRate <- c(0.0029)
time <- 3000
simul_NeutralSpatPatt(nsp,side,alfa,m,ReplRate,"S",time,10,10,"L",T,T)

saveGIF(simul_NeutralSpatPatt(nsp,side,alfa,m,ReplRate,"S",1100,10,850,"L",T,F), 
        interval = .5, 
        movie.name=paste0("neuL",nsp,"_",side,"R", ReplRate,".gif")
)

time <- 3000
simul_NeutralSpatPatt(nsp,side,alfa,m,ReplRate,"S",time,10,100,"U",T,T)

saveGIF(simul_NeutralSpatPatt(nsp,side,alfa,m,ReplRate,"S",1600,10,1350,"U",T,F), 
        interval = .5, 
        movie.name=paste0("neuU",nsp,"_",side,"R", ReplRate,".gif")
)

# Plot simulations
# Make video


```
