# The critical transition between neutral and competitive communities 

## Estimation of early warnings using the Max patch proportion, variance and Skewness

I use here the following neutral model with power dispersal kernel:

<https://github.com/lsaravia/Neutral>

I generate parameter files for the simulation of neutral/hierarchical model using a uniform and a logseries metacommunity distribution  


```{r setup, eval=T }
load(".RData")
#simul  <- F # variable to perform or not the simulations

oldcd <-getwd()
source("R/Neutral_fun.r")

# Set the location of the binary 
#
neuBin <- "~/Dropbox/cpp/CaNew/Neutral/ipsNeutralPow"
neuBin64<- "~/Dropbox/cpp/CaNew/Neutral/ipsNeutralP64"


require(pander)
require(plyr)
require(dplyr)

panderOptions('table.split.table',Inf)
panderOptions('table.style', 'multiline')
options("scipen"=100, "digits"=6)
```

## Plots of Smax - Calculation of Early warnings based on the Max Cluster (Smax)

```{r plotSmaxT20000_clu_side_64_meta_m1, eval=F,echo=F,message=T,warning=T}

m   <-0.1
alfa <-round(2.03897,5)
side <- 256
nsp <- 64
time <- 20000

require(plyr)
require(dplyr)
require(ggplot2)

# Select the critical points across sides (128,192,256) 
# 
k<-filter(rhoCritSide,Time==time,MetaNsp==nsp,DispersalDistance==round(mean_power(alfa),2),ColonizationRate==m,Side!=64)
k$MetaType <- factor(k$MetaType,labels=c("Logseries","Uniform"))


#
# Select clusters across sides (128,192,256)
#
tClusters <- Clusters %>% filter(MetaNsp==nsp,DispersalDistance==alfa,ColonizationRate==m,Side!=64)  %>% mutate(MetaType=factor(MetaType,labels=c("Logseries","Uniform")))

#
# Select colors 
#
require(RColorBrewer)
colp <-brewer.pal(8,"Dark2")


#
# Plot of Spanning clusters sizes with critical probability across side
#
ggplot(tClusters, aes(x=ReplacementRate, y=SpanningClust)) + geom_point(alpha=.1) + theme_bw() + scale_x_log10() + stat_summary(fun.y=mean,geom="line",colour=colp[1])+ facet_grid(Side ~ MetaType ) + ylab("Spanning Cluster Size") + xlab(bquote(rho)) + geom_vline(aes(xintercept=pcrit),k,colour=colp[6])
ggsave("figs/SpanClusRepl_T20000_64_side_meta_m1.png", width=6,height=6,units="in",dpi=600)

#
# The same Plot in linear x scale 
#
ggplot(tClusters, aes(x=ReplacementRate, y=SpanningClust)) + geom_point(alpha=.1) + theme_bw() + xlim(0,1)  + stat_summary(fun.y=mean,geom="line",colour=colp[1])+ facet_grid(Side ~ MetaType ) + ylab("Spanning Cluster Size") + xlab(bquote(rho)) + geom_vline(aes(xintercept=pcrit),k,colour=colp[6])
ggsave("figs/SpanClusRepl_T20000_64_side_meta_m1_lin.png", width=6,height=6,units="in",dpi=600)

#
# Plot of Max clusters proportion with critical probability across side 
#
ggplot(tClusters, aes(x=ReplacementRate, y=MaxClusterProp)) + geom_point(alpha=.1) + theme_bw() + scale_x_log10() + stat_summary(fun.y=mean,geom="line",colour=colp[1])+ facet_grid(Side ~ MetaType ) + ylab("Max. Cluster Size") + xlab(bquote(rho)) + geom_vline(aes(xintercept=pcrit),k,colour=colp[6])
ggsave("figs/MaxClusRepl_T20000_64_side_meta_m1.png", width=6,height=6,units="in",dpi=600)

#
# Plot of Max clusters proportion with critical probability
#
ggplot(tClusters, aes(x=ReplacementRate, y=MaxClusterProp)) + geom_point(alpha=.1) + theme_bw() + xlim(0,1) + stat_summary(fun.y=mean,geom="line",colour=colp[1])+ facet_grid(Side ~ MetaType ) + ylab("Max. Cluster Size") + xlab(bquote(rho)) + geom_vline(aes(xintercept=pcrit),k,colour=colp[6])
ggsave("figs/MaxClusRepl_T20000_64_side_meta_m1_lin.png", width=6,height=6,units="in",dpi=600)

# Select  Smax & Shannon diversity vs rho across ColonizationRate 
#
k<-filter(rhoCritSide,Time==time,MetaNsp==nsp,DispersalDistance==26.66,Side==256)
k$MetaType <- factor(k$MetaType,labels=c("Logseries","Uniform"))
tClusters <- Clusters %>% filter(MetaNsp==nsp,DispersalDistance==alfa,Side==256)  %>% mutate(MetaType=factor(MetaType,labels=c("Logseries","Uniform")))

#
# Smax vs rho
#
ggplot(tClusters, aes(x=ReplacementRate, y=MaxClusterProp)) + geom_point(alpha=.1) + theme_bw() + scale_x_log10() + stat_summary(fun.y=median,geom="line",colour=colp[1])+ facet_grid(ColonizationRate ~ MetaType,scales="free_y" )+xlab(bquote(rho)) + geom_vline(aes(xintercept=pcrit),k,colour=colp[6])
ggsave("figs/SmaxvsRepl_T20000_64_256_meta_m.png", width=6,height=6,units="in",dpi=600)

#
# Smax vs rho in linear x scale 
#
ggplot(tClusters, aes(x=ReplacementRate, y=MaxClusterProp)) + geom_point(alpha=.1) + theme_bw() +  stat_summary(fun.y=median,geom="line",colour=colp[1])+ facet_grid(ColonizationRate ~ MetaType,scales="free_y" )+xlab(bquote(rho)) + geom_vline(aes(xintercept=pcrit),k,colour=colp[6]) + theme(panel.margin.x=unit(0.6, "lines"))
ggsave("figs/SmaxvsRepl_T20000_64_256_meta_m_lin.png", width=6,height=6,units="in",dpi=600)


#
# Smax vs H
#
ggplot(tClusters, aes(x=MaxClusterProp, y=H)) + geom_point(alpha=.1) + theme_bw() +  scale_x_log10() +  facet_grid(ColonizationRate ~ MetaType,scales="free_y" )
  
ggsave("figs/SmaxvsH_T20000_64_256_meta_m.png", width=6,height=6,units="in",dpi=600)


#
# Smax vs Richness 
#
ggplot(tClusters, aes(x=MaxClusterProp, y=Richness)) + geom_point(alpha=.1) + theme_bw() +  scale_x_log10() +  facet_grid(ColonizationRate ~ MetaType,scales="free_y" )

rm(kk,k,k1,p,mClusters,tClusters,Clu,rank)

```


## Plots of Smax - Calculation of Early warnings based on the Max Cluster (Smax)

```{r plotSmaxT20000_clu_side_64_meta_m1, eval=F,echo=F,message=T,warning=T}

m   <-0.1
alfa <-round(2.03897,5)
side <- 256
nsp <- 64
time <- 20000

require(plyr)
require(dplyr)
require(ggplot2)


# Select  Smax & Shannon diversity vs rho across ColonizationRate 
#
k<-filter(rhoCritSide,Time==time,MetaNsp==nsp,DispersalDistance==26.66,Side==256)
k$MetaType <- factor(k$MetaType,labels=c("Logseries","Uniform"))

tClusters <- Clusters %>% filter(MetaNsp==nsp,DispersalDistance==alfa,Side==256)  %>% mutate(MetaType=factor(MetaType,labels=c("Logseries","Uniform"))) %>% group_by(MetaNsp,Side,MetaType,ColonizationRate,DispersalDistance,ReplacementRate) %>% summarise(MaxClusterVar=var(MaxClusterProp),MaxClusterProp=mean(MaxClusterProp),n=n(),SpanningProb=sum(ifelse(SpanningSpecies>0,1,0))/n,SpanningClust=mean(SpanningClust))

require(RColorBrewer)
colp <-brewer.pal(8,"Dark2")

ggplot(tClusters, aes(x=ReplacementRate, y=MaxClusterProp)) + geom_point() + theme_bw() + scale_x_log10() +   facet_grid(ColonizationRate ~ MetaType,scales="free_y" ) +xlab(bquote(rho)) + geom_line(colour=colp[1]) + geom_vline(aes(xintercept=pcrit),k,colour=colp[6]) + ylab("Mean of max cluster size")+  theme(axis.text.x=element_text(angle=-30, vjust=0.9,hjust = 0.1)) 
ggsave("figs/SmaxvsRepl_T20000_64_side_meta_m.png", width=6,height=6,units="in",dpi=600)

ggplot(tClusters, aes(x=ReplacementRate, y=MaxClusterVar)) + geom_point() + theme_bw() + scale_x_log10() +   facet_grid(ColonizationRate ~ MetaType,scales="free_y" ) +xlab(bquote(rho)) + geom_line(colour=colp[1]) + geom_vline(aes(xintercept=pcrit),k,colour=colp[6]) + ylab("Mean of max cluster size")+  theme(axis.text.x=element_text(angle=-30, vjust=0.9,hjust = 0.1)) 
ggsave("figs/VarSmaxvsRepl_T20000_64_side_meta_m.png", width=6,height=6,units="in",dpi=600)


#
# Calculate fluctuations.
# 
require(fitdistrplus)
tClusters <- Clusters %>% filter(MetaNsp==nsp,DispersalDistance==alfa,Side==256)  %>% mutate(MetaType=factor(MetaType,labels=c("Logseries","Uniform"))) %>% group_by(MetaNsp,Side,MetaType,ColonizationRate,DispersalDistance,ReplacementRate) %>% mutate( Mean_MaxClusterProp=mean(MaxClusterProp), Delta_MaxCluster=MaxClusterProp-Mean_MaxClusterProp)

# Plot fluctuations
#
ggplot(tClusters, aes(x=ReplacementRate, y=Delta_MaxCluster)) + geom_point(alpha=.1) + theme_bw() + scale_x_log10() +   facet_grid(ColonizationRate ~ MetaType,scales="free_y" ) +xlab(bquote(rho)) + stat_summary(fun.y=median,geom="line",colour=colp[1]) + geom_vline(aes(xintercept=pcrit),k,colour=colp[6]) + ylab("Fluctuations of max cluster size")+  theme(axis.text.x=element_text(angle=-30, vjust=0.9,hjust = 0.1)) 
ggsave("figs/DeltaSmaxvsRepl_T20000_64_side_meta_m.png", width=6,height=6,units="in",dpi=600)

# Variance of fluctuations
#
vClusters <- tClusters %>% summarise(varDelta_MaxCluster=var(Delta_MaxCluster))
ggplot(vClusters, aes(x=ReplacementRate, y=varDelta_MaxCluster)) + geom_point(size=1) + theme_bw() + scale_x_log10() +   facet_grid(ColonizationRate ~ MetaType,scales="free_y" ) +xlab(bquote(rho)) + geom_line(colour=colp[1]) + geom_vline(aes(xintercept=pcrit),k,colour=colp[6]) + ylab(expression(Variance~of~Delta~S[max]))+  theme(axis.text.x=element_text(angle=-30, vjust=0.9,hjust = 0.1)) 
ggsave("figs/VarDeltaSmaxvsRepl_T20000_64_side_meta_m.png", width=6,height=6,units="in",dpi=600)

# Skewness of fluctuations
#
sClusters <- tClusters %>% do(abs_skewness=(descdist(.$MaxClusterProp, discrete=FALSE, boot=500))$skewness)
sClusters$abs_skewness <- as.numeric(sClusters$abs_skewness)

ggplot(sClusters, aes(x=ReplacementRate, y=abs_skewness)) + geom_point(size=1) + theme_bw() + scale_x_log10() +   facet_grid(ColonizationRate ~ MetaType,scales="free_y" ) +xlab(bquote(rho)) + geom_vline(aes(xintercept=pcrit),k,colour=colp[6]) + ylab("Skewness of Delta Smax")+ geom_hline(yintercept = 0,colour=colp[1]) + theme(axis.text.x=element_text(angle=-30, vjust=0.9,hjust = 0.1)) 

ssClusters <-left_join(sClusters,k,by=c("MetaType","ColonizationRate","Side","MetaNsp")) %>% mutate(before=ifelse(ReplacementRate<pcrit,TRUE,FALSE))

ggplot(ssClusters, aes(x=ReplacementRate, y=abs_skewness,colour=before)) + geom_point(size=1) + theme_bw() + scale_color_manual(values=colp,guide=FALSE) + scale_x_log10() +   facet_grid(ColonizationRate ~ MetaType,scales="free_y" ) +xlab(bquote(rho)) + geom_vline(aes(xintercept=pcrit),k,colour=colp[6]) + ylab(expression(Skewness~of~Delta~S[max]))+ geom_hline(yintercept = 0,colour=colp[1]) + theme(axis.text.x=element_text(angle=-30, vjust=0.9,hjust = 0.1)) 
ggsave("figs/SkewDeltaSmaxvsRepl_T20000_64_side_meta_m.png", width=6,height=6,units="in",dpi=600)


```


# OLD CODE : Simulate to estimate distributions of patch sizes statistics


```{r simuldisp26_cluAll_side_64_meta30_T5000, eval=F,echo=F,message=T,warning=T}
setwd(oldcd)
source("R/powerlaw/discpowerexp.R")
source("R/powerlaw/discexp.R")
source("R/powerlaw/powerexp.R")
source("R/powerlaw/exp.R")
source("R/powerlaw/pareto.R")
source("R/powerlaw/zeta.R")

setwd("Simul")


m <-  0.0001596079
alfa <- 2.038974
side <- 256
nsp <- 64
nSimul <- 10
time <- 5000
#time <- 100
ReplRate <- c(0.0000,0.0005,0.0010,0.0020,0.0030,0.004,0.005,0.01)
p <-expand.grid(disp=alfa,migr=m,repl=ReplRate,side=c(256),meta=c("U","L")) 

require(doParallel)
cn <-detectCores()
cl <- makeCluster(cn)
registerDoParallel(cl)
Models <- data.frame()
Mdl <- data.frame()
Mdl <- foreach(i=1:nrow(p),.combine='rbind') %dopar%
{
    simulNeutral_Clusters(nsp,p$side[i],p$disp[i],p$migr[i],p$repl[i],"A",time,nSimul,F,"N",p$meta[i],F)
}

stopCluster(cl)
setwd(oldcd)

Models <- rbind(Models,Mdl)

rm(cn,cl,Mdl,p)

save.image()

```


# Plot the cluster sizes with fitted functions
 
```{r plotFitdisp26_cluAll_side_64_meta30_T5000, eval=F,echo=F,message=T,warning=T}
source("R/powerlaw/discpowerexp.R")
source("R/powerlaw/discexp.R")
source("R/powerlaw/powerexp.R")
source("R/powerlaw/exp.R")
source("R/powerlaw/pareto.R")
source("R/powerlaw/zeta.R")

setwd("Simul")


m <-  0.0001596079
alfa <- 2.038974
side <- 256
nsp <- 64
nSimul <- 10
time <- 5000
ReplRate <- c(0.0000,0.0005,0.0010,0.0020,0.0030,0.004,0.005,0.01)
p <-expand.grid(disp=alfa,migr=m,repl=ReplRate,side=c(256),meta=c("U","L")) 

for(i in 1:nrow(p)){
  plotNeutral_Clusters(nsp,p$side[i],p$disp[i],p$migr[i],p$repl[i],time,p$meta[i],Models)
}
setwd(oldcd)

```

# Plot relation of power exponent/ exponential rate with ReplacementRate

```{r plotdisp26_cluAll_side_64_meta30_T5000, eval=F,echo=F,message=T,warning=T}
setwd(oldcd)

#
# Hacer grafico con proporcion de ajustes 
require(ggplot2)
require(plyr)
require(dplyr)
Models <- ungroup(Models)


# Power laws best models 
#
nMdl <-group_by(Models,MortalityRate,DispersalDistance,ColonizationRate,ReplacementRate,MetaType,Rep) %>% filter(DeltaAIC>0, model=="PowExp")

# Proportion of best models by model only
#
group_by(Models,model) %>% filter(DeltaAIC==0)  %>% summarise(n=n()) %>% ungroup() %>% mutate(Frequency=n/sum(n))

namType <- c("Spanning","MaxPatch","Other MaxPatch","Other Spanning")
namTypeAb <- c("Spanning/+Abundant","Spanning/+Abundant","Other Species","Other Species")

mMdl <- group_by(Models,model,type) %>% filter(DeltaAIC==0)  %>% summarise(n=n()) %>% ungroup() %>% mutate(Frequency=n/sum(n),type=namType[type])

mc <- c("#E69F00", "#56B4E9", "#009E73", "#F0E442", "#0072B2", "#D55E00", "#CC79A7")
ggplot(mMdl, aes(x=model,y=Frequency,fill=type)) + geom_bar(stat="identity") +  scale_fill_manual(values=mc,name="Species",breaks=c("Spanning","MaxPatch","Other Spanning","Other MaxPatch")) + scale_x_discrete(labels=c("No Model","Power","Power Exp.")) + theme_bw()
ggsave("figs/ClusModels_T5000_64_256_Logser.png", width=6,height=6,units="in",dpi=600)

require(pander)
pandoc.table(mMdl,round=2)


# Select Power w/exponential cutoff other sp most abundant or other spanning
#
mMdl <- filter(Models,model=="PowExp",type==3 | type==4) %>% mutate(typeAb=namTypeAb[type],type=namType[type])

# Plot lambda - exponential decay rate
#
ggplot(mMdl,aes(x=ReplacementRate,y=rate,colour=type)) + geom_point() +  theme_bw() + facet_wrap(~MetaType,scales="free_y") + stat_summary(fun.y=median,geom="line",colour=mc[5],linetype="dashed") + scale_x_continuous(breaks=c(0,0.0010,0.0020,0.0030,0.005,0.01)) +
  theme(axis.text.x=element_text(angle=90,vjust=0.5)) + ylab(bquote(lambda)) + xlab(bquote(rho))+ scale_colour_manual(values=mc) +stat_quantile(alpha=0.5) + coord_cartesian(ylim=c(-0.02,0.65))
ggsave("figs/discRateOther_T5000_64_256_meta.png", width=7,height=4,units="in",dpi=600)

# Quantile regression lambda
#
#
rqm <-group_by(mMdl,type,MetaType) %>%
      do(as.data.frame(do.call(rbind,
                               lapply(summary(rq(rate~ReplacementRate,data=.,tau=c(.25, .5, .75)),se="boot"),coef))
                       ,row.names= NULL)) %>% mutate(Tau=rep(c(.25, .5, .75),each=2),param="lambda")


# Plot power exponent alpha
#
mMdl <- filter(Models,model=="PowExp",type==3 | type==4) %>% mutate(typeAb=namTypeAb[type],type=namType[type])

ggplot(mMdl,aes(x=ReplacementRate,y=alfa,colour=type)) + geom_point() +  theme_bw() + facet_wrap(~MetaType,scales="free_y") + stat_summary(fun.y=median,geom="line",colour=mc[5],linetype="dashed") + scale_x_continuous(breaks=c(0,0.0010,0.0020,0.0030,0.005,0.01)) +
  theme(axis.text.x=element_text(angle=90,vjust=0.5)) + ylab(bquote(alpha)) + xlab(bquote(rho))+ scale_colour_manual(values=mc)+stat_quantile(alpha=0.5)+ coord_cartesian(ylim=c(1.1,2.1))

ggsave("figs/discExpOther_T5000_64_256_meta.png", width=7,height=4,units="in",dpi=600)


# Quantile regression alpha
#
#
rq1 <-group_by(mMdl,type,MetaType) %>%
      do(as.data.frame(do.call(rbind,
                               lapply(summary(rq(alfa~ReplacementRate,data=.,tau=c(.25, .5, .75)),se="boot"),coef))
                       ,row.names= NULL)) %>% mutate(Tau=rep(c(.25, .5, .75),each=2),param="alpha")

rqm <- rbind(rqm,rq1)

# Select Power w/exponential cutoff - spanning or most abundant  sp
#
mMdl <- filter(Models,model=="PowExp",type==1 | type==2) %>% mutate(typeAb=namTypeAb[type],type=namType[type])


# Plot Power exponent - alpha  of spanning or most abundant  sp
#
ggplot(mMdl,aes(x=ReplacementRate,y=alfa,colour=type)) + geom_point() +  theme_bw() + facet_wrap(~MetaType,scales="free_y") + stat_summary(fun.y=mean,geom="line",colour=mc[5],linetype="dashed") + scale_x_continuous(breaks=c(0,0.0010,0.0020,0.0030,0.005,0.01)) +
  theme(axis.text.x=element_text(angle=90,vjust=0.5)) + ylab(bquote(alpha)) + xlab(bquote(rho)) + scale_colour_manual(values=mc)+stat_quantile(alpha=0.5)+ coord_cartesian(ylim=c(1.5,3.6))
ggsave("figs/discExpSpan_T5000_64_256_meta.png", width=7,height=4,units="in",dpi=600)

# Quantile regression alpha
#
#
rq1 <-group_by(mMdl,type,MetaType) %>%
      do(as.data.frame(do.call(rbind,
                               lapply(summary(rq(alfa~ReplacementRate,data=.,tau=c(.25, .5, .75)),se="boot"),coef))
                       ,row.names= NULL)) %>% mutate(Tau=rep(c(.25, .5, .75),each=2),param="alpha")

rqm <- rbind(rqm,rq1)

# Select Power w/exponential cutoff - spanning or most abundant  sp
#
mMdl <- filter(Models,model=="PowExp",type==1 | type==2) %>% mutate(typeAb=namTypeAb[type],type=namType[type])

# Plot Exponential rate - lambda of spanning or  most abundant sp
#
ggplot(mMdl,aes(x=ReplacementRate,y=rate,colour=type)) + geom_point() +  theme_bw() + facet_wrap(~MetaType,scales="free_y") + stat_summary(fun.y=mean,geom="line",colour=mc[5],linetype="dashed") + scale_x_continuous(breaks=c(0,0.0010,0.0020,0.0030,0.005,0.01)) +
  theme(axis.text.x=element_text(angle=90,vjust=0.5)) + ylab(bquote(lambda)) + xlab(bquote(rho))+ scale_colour_manual(values=mc)+stat_quantile(alpha=0.5)+ coord_cartesian(ylim=c(-0.02,0.32))
ggsave("figs/discRateSpan_T5000_64_256_meta.png", width=7,height=4,units="in",dpi=600)

# Quantile regression lambda
#
#
rq1 <-group_by(mMdl,type,MetaType) %>%
      do(as.data.frame(do.call(rbind,
                               lapply(summary(rq(rate~ReplacementRate,data=.,tau=c(.25, .5, .75)),se="boot"),coef))
                       ,row.names= NULL)) %>% mutate(Tau=rep(c(.25, .5, .75),each=2),param="lambda")

rqm <- rbind(rqm,rq1)
rqm$slope<-c(F,T)
names(rqm)[6]<-"pvalue"
rqm <- filter(rqm, slope==T ) %>% #rename(species=type) %>%
  select(MetaType,species,param,Tau,Value:pvalue)

require(pander)
pandoc.table(rqm,round=2)
group_by(rqm,MetaType,type,param) %>% filter(pvalue<0.05) %>% summarise(n=n())


```

# Simulations to make a video of percolation

```{r gensimul_spat_256_32_meta30_T5000, eval=F,echo=F,message=T,warning=T}
setwd("Simul")

m =  0.0001596079
alfa=2.038974
side <- 256
nsp <- 32
nSimul <- 1


ReplRate <- c(0.0011)
time <- 3000

require(animation)
# simul_NeutralSpatPatt <- function(nsp,side,disp,migr,repl,clus="S",time=1000,inter=10,init=1,meta="L",delo=F,sim=T,sedIni=0,modType=4,death=0.2,birth=1,colPal=0) 

simul_NeutralSpatPatt(nsp,side,alfa,m,ReplRate,"S",time,10,100,"L",T,T,2)

saveGIF(simul_NeutralSpatPatt(nsp,side,alfa,m,ReplRate,"S",1000,10,800,"L",T,F), 
        interval = .3, 
        movie.name=paste0("neuL",nsp,"_",side,"R", ReplRate,".gif")
)


ReplRate <- c(0.0029)
time <- 3000
simul_NeutralSpatPatt(nsp,side,alfa,m,ReplRate,"S",time,10,10,"L",T,T)

saveGIF(simul_NeutralSpatPatt(nsp,side,alfa,m,ReplRate,"S",1100,10,850,"L",T,F), 
        interval = .5, 
        movie.name=paste0("neuL",nsp,"_",side,"R", ReplRate,".gif")
)

time <- 3000
simul_NeutralSpatPatt(nsp,side,alfa,m,ReplRate,"S",time,10,100,"U",T,T)

saveGIF(simul_NeutralSpatPatt(nsp,side,alfa,m,ReplRate,"S",1600,10,1350,"U",T,F), 
        interval = .5, 
        movie.name=paste0("neuU",nsp,"_",side,"R", ReplRate,".gif")
)

# Plot simulations
# Make video


```
